\bf\mftitle

### 2011-03-01 doc/jInfer/architecture/architecture.tex
architecture final touch

The first stands for a bare node in XML document tree, it has its name and context within the tree (path from root).
The latter two extend \code{NamedNode} interface.
\code{StructuralNode} is for nodes which form structure of XML document tree: elements and text nodes.
\code{ContentNode} is for nodes that have content in XML documents: text nodes and attributes.
We have three classes: \code{Element} for elements, \code{SimpleData} for text nodes, \code{Attribute} for attributes (see package \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes}).
In theory, the classes and interfaces would be layed out as in fig. \ref{interfaces_nodes}
\begin{figure}
\centering\includegraphics[scale=\myscale]{interfaces_nodes}
\caption{How should interfaces and classes for XML representation look like in theory} \label{interfaces_nodes}
\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes}
\caption{How are interfaces and classes for XML representation arranged in practice} \label{nodes}
\end{figure}
% This figure has been replaced by UML-like
%\begin{figure}
%\centering\includegraphics[scale=\myscale]{nodes_full}
%\caption{XML representing interfaces and classes in detail} \label{nodes_full}
%\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes_full2}
\caption{Class diagram for XML representing interfaces and classes} \label{nodes_full2}
\end{figure}

@@

As in regular expressions, classes pertaining to XML nodes are by default immutable.
For elements, it means no adding of attributes and changing regexp reference (regexp instance itself is immutable as well).
The same \code{getMutable()} principles and good usage practises hold for these classes.

@@

To fulfil symbol conversion, one have to provide implementation of \code{AutomatonClonerSymbolConverter<A, B>} interface.
Interface has one method.
\begin{verbatim}
	B convertSymbol(final A symbol);
\end{verbatim}
Its purpose is to provide mapping from symbol over one domain to new symbols.
Implementation has to be \code{equals()} consistent, if in first automaton are two transitions with symbols \code{a}, \code{b} such that
\code{a.equals(b) == true}, converter has to produce new symbols that are equal.

@@

	For element person, even when simplified grammar specifies its occurence to at least once, at most 3 times, as DTD has no such construct, export module have to do some magic. Situation is even worse for elements that contain simple data inside simplified rule. Only way to express mixed content in DTD is to use \verb.(#PCDATA | note)*. construct. Even if regular expression is complicated, export module has to do this "flattening".texmaker

@@

	This is basically done by calling \code{cz.cuni.mff.ksi.jinfer.base.interfaces.Expander} interface method \code{expand()}. One can implement own intelligent expander, or use our provided\\ \code{cz.cuni.mff.ksi.jinfer.basicigg.expansion.ExpanderImpl}.

@@

\code{SchemaGeneratorCallback.finished()} has two \code{String}s as arguments: \code{schema} is the actual string representation of the resulting schema, \code{extension} is a file extension of the result (such as "dtd" or "xsd") which the framework will use when saving the result in a file.

@@

At the present, jInfer modules use the following metadata, all defined in \code{IGGUtils} class:
\begin{itemize}
	\item \code{from.xml}, filled in by \jmodule{BasicIGG} module: means that this rule was created (originates from) from a XML document.
	\item \code{from.schema}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created (originates from) from a schema.
	\item \code{from.query}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created from a query.
	\item \code{is.sentinel}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: when importing XML document, one can build whole tree in memory (as in fig. \ref{xml_example}) and then construct list of rules from it (thus saving memory). With schema import however, one not only doesn't know right side of rule in advance (solved by stack in XML import), but right side can be defined anywhere in source file. To save complicated loading of whole schema, searching and pairing elements thorough rules, nodes on right side of rule are created empty - holding only name of node. Fact, that this node has no more information than it's name and position on right side of rule is denominated by labeling the node as sentinel.
	\item \code{required}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: indicates that the attribute is required.
\end{itemize}
All of these metadata are of set/not set character (using \code{Boolean.TRUE} as value, but their presence effectively means "true").

@@

For this reason, inference modules extend the \code{Capabilities} interface defining a single method: \code{getCa\.pa\.bi\.li\.ties()}. This method returns a list of strings representing the abilities, or "capabilities" of this module.
An inference module can query the capabilities of the \emph{next} module in the inference chain by invoking the 
\begin{verbatim}
RunningProject.getNextModuleCaps()
\end{verbatim}
method to obtain the next module encapsulated in the \code{Capabilities} interface.

@@

Example of Capabilities usage taken from \jmodule{XSDImporter} module:
\begin{verbatim}
// if the next module cannot handle complex regexps, help it by expanding our result
if (!RunningProject.getNextModuleCaps().getCapabilities()
             .contains(Capabilities.CAN_HANDLE_COMPLEX_REGEXPS)) { 
  // lookup expander
  final Expander expander = Lookup.getDefault().lookup(Expander.class);
  // return expanded
  return expander.expand(parser.getRules());
}
// return not expanded rules
return parser.getRules();
\end{verbatim}

@@

\noindent Base modules:
\begin{itemize}
	\item \jmodule{jInfer}: not a NBP module in fact, but rather a module suite - the ``root" NB project for the whole framework.
	\item \jmodule{Base}: contains common data structures, interfaces and utility logic shared across all other modules.
\end{itemize}

@@

%\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}

>>>>

The first stands for a bare node in XML document tree, it has its name and context within the tree (path from root).
The latter two extend \code{NamedNode} interface.
\code{StructuralNode} is for nodes which form structure of XML document tree: elements and text nodes.
\code{ContentNode} is for nodes that have content in XML documents: text nodes and attributes.
We have three classes: \code{Element} for elements, \code{SimpleData} for text nodes, \code{Attribute} for attributes (see package \code{cz.cuni.mff.ksi.jinfer.base.objects.nodes}).
In theory, the classes and interfaces would be layed out as in fig. \ref{interfaces_nodes}
\begin{figure}
\centering\includegraphics[scale=\myscale]{interfaces_nodes}
\caption{How should interfaces and classes for XML representation look like in theory} \label{interfaces_nodes}
\end{figure}
\begin{figure}
\centering\includegraphics[scale=\myscale]{nodes}
\caption{How are interfaces and classes for XML representation arranged in practice} \label{nodes}
\end{figure}
% This figure has been replaced by UML-like
%\begin{figure}
%\centering\includegraphics[scale=\myscale]{nodes_full}
%\caption{XML representing interfaces and classes in detail} \label{nodes_full}
%\end{figure}
\begin{figure}
\centering\includegraphics[width=\textwidth]{nodes_full2}
\caption{Class diagram for XML representing interfaces and classes} \label{nodes_full2}
\end{figure}

@@

As in regular expressions, classes pertaining to XML nodes are by default immutable.
For elements, it means no adding of attributes and changing regexp reference (regexp instance itself is immutable as well).
The same \code{get\.Mu\.tab\.le()} principles and good usage practises hold for these classes.

@@

To fulfil symbol conversion, one have to provide implementation of \code{AutomatonClonerSymbolConverter<A, B>} interface.
Interface has one method.
\begin{verbatim}
	B convertSymbol(A symbol);
\end{verbatim}
Its purpose is to provide mapping from symbol over one domain to new symbols.
Implementation has to be \code{equals()} consistent, if in first automaton are two transitions with symbols \code{a}, \code{b} such that
\code{a.equals(b) == true}, converter has to produce new symbols that are equal.

@@

	For element person, even when simplified grammar specifies its occurence to at least once, at most 3 times, as DTD has no such construct, export module have to do some magic. Situation is even worse for elements that contain simple data inside simplified rule. Only way to express mixed content in DTD is to use \verb.(#PCDATA | note)*. construct. Even if regular expression is complicated, export module has to do this ``flattening''.texmaker

@@

This is basically done by calling \code{cz.cuni.mff.ksi.jinfer.base.interfaces.Expander} interface method \code{ex\.pand()}. One can implement own intelligent expander, or use our provided \code{cz.cuni.mff.ksi.jinfer.basic\.igg.ex\.pansion.ExpanderImpl}.

@@

\code{SchemaGeneratorCallback.finished()} has two \code{String}s as arguments: \code{schema} is the actual string representation of the resulting schema, \code{extension} is a file extension of the result (such as ``dtd'' or ``xsd'') which the framework will use when saving the result in a file.

@@

At the present, jInfer modules use the following metadata, all defined in \code{IGGUtils} class:
\begin{itemize}
	\item \code{from.xml}, filled in by \jmodule{BasicIGG} module: means that this rule was created (originates from) from a XML document.
	\item \code{from.schema}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created (originates from) from a schema.
	\item \code{from.query}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: means that this rule was created from a query.
	\item \code{is.sentinel}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: when importing XML document, one can build whole tree in memory (as in fig. \ref{xml_example}) and then construct list of rules from it (thus saving memory). With schema import however, one not only doesn't know right side of rule in advance (solved by stack in XML import), but right side can be defined anywhere in source file. To save complicated loading of whole schema, searching and pairing elements thorough rules, nodes on right side of rule are created empty - holding only name of node. Fact, that this node has no more information than it's name and position on right side of rule is denominated by labeling the node as sentinel.
	\item \code{required}, filled in by \jmodule{BasicIGG} and \jmodule{XSDImporter} modules: indicates that the attribute is required.
\end{itemize}
All of these metadata are of set/not set character (using \code{Boolean.TRUE} as value, but their presence effectively means ``true'').

@@

For this reason, inference modules extend the \code{Capabilities} interface defining a single method: \code{getCa\.pa\.bi\.li\.ties()}. This method returns a list of strings representing the abilities, or ``capabilities'' of this module.
An inference module can query the capabilities of the \emph{next} module in the inference chain by invoking the 
\begin{verbatim}
RunningProject.getNextModuleCaps()
\end{verbatim}
method to obtain the next module encapsulated in the \code{Capabilities} interface.

@@

Example of Capabilities usage taken from \jmodule{XSDImporter} module:
\begin{verbatim}
// if the next module cannot handle complex regexps, help it by expanding our result
if (!RunningProject.getNextModuleCaps().getCapabilities()
             .contains(Capabilities.CAN_HANDLE_COMPLEX_REGEXPS)) { 
  // lookup expander
  Expander expander = Lookup.getDefault().lookup(Expander.class);
  // return expanded
  return expander.expand(parser.getRules());
}
// return not expanded rules
return parser.getRules();
\end{verbatim}

@@

\noindent Base modules:
\begin{itemize}
	\item \jmodule{jInfer}: not a NBP module in fact, but rather a module suite - the ``root'' NB project for the whole framework.
	\item \jmodule{Base}: contains common data structures, interfaces and utility logic shared across all other modules.
\end{itemize}

@@

\paragraph{}
Another use of tokens is \code{cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer} representing a module providing a rule displayer. This token is provided by \jmodule{BasicRuleDisplayer} and \jmodule{TreeRuleDisplayer}, requested by \jmodule{BasicIGG}, \jmodule{XSDImporter} and \jmodule{TwoStepSimplifier}.

\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
